---
title: "Basic Time Series"
author: "Rahadian Arthapati"
date: "1/3/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Introduction
Time series is a sequence of data in chronological order. Data is commonly recorded sequentially, over time. 

```{r}
library(tidyr)

data(AirPassengers)
class(AirPassengers)
```

```{r}
# Plot AirPassengers
plot(AirPassengers)

# View the start and end dates of AirPassengers
start(AirPassengers)
end(AirPassengers)

# Use time(), deltat(), frequency(), and cycle() with AirPassengers 
time(AirPassengers)
deltat(AirPassengers)
frequency(AirPassengers)
cycle(AirPassengers)

plot(AirPassengers)
abline(reg=lm(AirPassengers~time(AirPassengers)))

plot(aggregate(AirPassengers,FUN = mean))
boxplot(AirPassengers~cycle(AirPassengers))

```
# When is the sampling frequency exact?

The sampling frequency is often only approximate and the interval between observations is not quite a fixed unit. For example, there are usually 365 days in a year based on the Gregorian calendar. However, (almost) every four years there are 366 days (leap years).

As a simplifying assumption, we often ignore these small discrepancies and proceed as though the sampling frequency and observation intervals are fixed constants. Typically, our results will not be sensitive to approximation when the underlying process is not changing too quickly.

# Missing values
```{r}
# Plot the AirPassengers data
plot(AirPassengers)

# Compute the mean of AirPassengers
# Impute mean values to NA in AirPassengers
AirPassengers[85:96] <- mean(AirPassengers, na.rm = T)

# Generate another plot of AirPassengers
plot(AirPassengers)

# Add the complete AirPassengers data to your plot
rm(AirPassengers)
points(AirPassengers, type = "l", col = 2, lty = 3)
```
# Creating a time series object with ts()
```{r}
data_vector = c(10,5,6,8,9,7,4,6,10,5,6,8,9,7,4,6,10,5,6,8,9,7,4,6,10,5,6,8,9,7,4,6)
time_series = ts(data_vector, start = 2000,end = 2018, frequency = 2)
is.ts(time_series)
plot(time_series)
```

